Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-17 Paperfolder/Paperfolder.Rmd
Updated paper folder would be sent to coauthors

  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.

@@

Eastern Asian populations were reported to have higher burden from either mortality or morbidity from stroke than populations in European or American regions [@Kim2014]. Dairy food, especially milk has been suggested to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in the Western countries [@Saito2019]. Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], whether people with such a low level intake of milk can still benefit against stroke would be questionable. Even if there is any benefit, not every individual with habitual milk intake can avoid dying from stroke. A more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay a stroke event or lower the hazard of dying from stroke. Accelerated failure time models under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model and can directly show how faster/slower individuals in an exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was sponsored by the Ministry of Education, Sports, Science, and Technology of Japan. Sampling methods and details about the JACC study have been described extensively in the literature [@Ohno2001; @Tamakoshi2005; @Tamakoshi2013]. Participants of the JACC study completed self-administered questionnaires about their lifestyles, food intake (food frequency questionnaire, FFQ), and medical histories of cardiovascular disease or cancer. In the final follow-up of the JACC study, data from a total of 110585 individuals (46395 men and 64190 women) were successfully retained for the current analysis. We further excluded samples if they meet one of the following criteria: 1) with any disease history of stroke, cancer, myocardial infarction, ischemic heart disease, or other types heart disease (n = 6655, 2931 men and 3724 women); 2) did not answer the question regarding their milk consumption in the baseline FFQ survey (n = 9545, 3593 men and 5952 women). Finally, 94385 (39386 men and 54999 women) are left in the database. The study design and informed consent procedure were approved by the Ethics Review Committee of Nagoya University School of Medicine.

@@

We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake. Age-adjusted stroke mortality rate were expressed as per 1000 person-year through the poisson regression model.

Full parametric proportional hazard models under Bayesian framework with Weibull distribution were fitted using Just Another Gibbs Sampler (JAGS) program [@Plummer2003] version 4.3.0 in R version 4.0.1 [@RCT2020]. JAGS program is similar to the OpenBUGS [@Lunn2009] project that uses a Gibbs sampling engine for MCMC simulation. In the current analysis, we specified non-informative prior distributions for each of the parameters in our models ($\beta_n \sim N(0, 1000)$, and $\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)$). The Brooks-Gelman-Rubin diagnostic [@Brooks1998] was used to refine the approximate point of convergence, the point when the ratio of the chains is stable around 1 and the within and between chain variability start to reach stability was visually checked. The auto-correlation tool further identified if convergence has been achieved or if a high degree of auto-correlation exists in the sample. Then, the number of iterations discarded as ‘burn-in’ was chosen. All models had a posterior sample size of 100000 from four separated chains with a "burn-in" of 2500 iterations. Posterior means (sd) and 95% Credible Intervals (CrI) of the estimated hazard ratios (HRs) as well as acceleration factors (AFs) were presented for each category of milk intake frequency taking the "never" category as the reference. Posterior probabilities that the estimated hazard of dying from stroke for the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $P(\text{HR} < 1)$.

@@

The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women). Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women). Age-adjusted stroke mortality rate for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women. Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among both sex.

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models. Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers. Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women. However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers. Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior AFs and HRs that was distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.

@@

<!-- - strength and limitation of current study -->
Some limitations here are worth mentioning. First, the milk intake frequency as well as other lifestyle information was collected only once at the baseline and was self-reported. Apparently habits in life are possible to alter over the time and these would resulted in misclassfication and residual confoudings. Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable. Therefore, we did not try to compute the amount of consumption by multiplying an average volume per occasion with the frequency of intake since the random error might be exaggerated and the observed associations may have attenuated. Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation. Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulation.

In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk. Time before an event of stroke mortality occurred were slowed down and delayed among men who drank milk regularly.

>>>>

  The authors declare no conflict of interest. The funding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.

@@

Eastern Asian populations were reported to have higher burden from either mortality or morbidity from stroke than populations in European or American regions [@Kim2014]. Dairy food, especially milk has been suggested to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in Western countries [@Saito2019]. Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], whether people with such a low level intake of milk can still benefit against stroke would require elucidation. A more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke. Accelerated failure time models under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model and can directly show how faster/slower individuals in one exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was sponsored by the Ministry of Education, Sports, Science, and Technology of Japan. Sampling methods and details about the JACC study have been described extensively in the literature [@Ohno2001; @Tamakoshi2005; @Tamakoshi2013]. Participants of the JACC study completed self-administered questionnaires about their lifestyles, food intake (food frequency questionnaire, FFQ), and medical histories of cardiovascular disease or cancer. In the final follow-up of the JACC study, data from a total of 110585 individuals (46395 men and 64190 women) were successfully retained for the current analysis. We further excluded samples if they meet one of the following criteria: 1) with any disease history of stroke, cancer, myocardial infarction, ischemic heart disease, or other types heart disease (n = 6655, 2931 men and 3724 women); 2) did not answer the question regarding their milk consumption in the baseline FFQ survey (n = 9545, 3593 men and 5952 women). Finally, 94385 (39386 men and 54999 women) are left in the database. The study design and informed consent procedure were approved by the Ethics Review Committee of Hokkaido University School of Medicine.

@@

We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake. Age-adjusted stroke mortality rate were expressed as per 1000 person-year predicted through poisson regression models.

Full parametric proportional hazard models under Bayesian framework with Weibull distribution were fitted using Just Another Gibbs Sampler (JAGS) program [@Plummer2003] version 4.3.0 in R version 4.0.1 [@RCT2020]. JAGS program is similar to the OpenBUGS [@Lunn2009] project that uses a Gibbs sampling engine for MCMC simulation. In the current analysis, we specified non-informative prior distributions for each of the parameters in our models ($\beta_n \sim N(0, 1000)$, and $\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)$). The Brooks-Gelman-Rubin diagnostic [@Brooks1998] was used to refine the approximate point of convergence, the point when the ratio of the chains is stable around 1 and the within and between chain variability start to reach stability was visually checked. The auto-correlation tool further identified if convergence has been achieved or if a high degree of auto-correlation exists in the sample. Then, the number of iterations discarded as ‘burn-in’ was chosen. All models had a posterior sample size of 100000 from four separated chains with a "burn-in" of 2500 iterations. Posterior means (sd) and 95% Credible Intervals (CrI) of the estimated hazard ratios (HRs) as well as acceleration factors (AFs) were presented for each category of milk intake frequency taking the "never" category as the reference. Posterior probabilities that the estimated hazard of dying from stroke for the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $Pr(\text{HR} < 1)$.

@@

The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women). Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women). Age-adjusted stroke mortality rates for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women. Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among both sexes.

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models. Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers. Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women. However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers. Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.

@@

<!-- - strength and limitation of current study -->
Some limitations here are worth mentioning. First, the milk intake frequency as well as other lifestyle information was collected only once at the baseline and was self-reported. Apparently life habits are possible to alter over time and these would resulted in misclassfication and residual confoundings. Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable. Therefore, we did not try to compute the amount of consumption by multiplying an average volume per occasion with the frequency of intake since the random error might be exaggerated and the observed associations may have attenuated. Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation. Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulations.

In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke particularly cerebral infarction compared with their counterparts who never consumed milk. Time before an event of stroke mortality occurred were slowed down and delayed among men who drank milk regularly.

### 2020-07-17 Paperfolder/Paperfolder.tex
Updated paper folder would be sent to coauthors

Eastern Asian populations were reported to have higher burden from
either mortality or morbidity from stroke than populations in European
or American regions \citep{Kim2014}. Dairy food, especially milk has
been suggested to reduce stroke risk by nearly 7\% for each 200 g
increment of daily consumption \citep{DeGoede2016}. Although 2 daily
servings of milk or dairy products is recommended in Japan
\citep{Yoshiike2007}, the actual per capita intake (\(\approx\) 63
g/day) of these food groups is much lower and less frequent than that in
the Western countries \citep{Saito2019}. Given that previous reports
have also indicated no significant
\citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
associations \citep{Larsson2009}, whether people with such a low level
intake of milk can still benefit against stroke would be questionable.
Even if there is any benefit, not every individual with habitual milk
intake can avoid dying from stroke. A more intuitive interpretation
would be available if we were able to show the probabilities and how
certain the existing data can provide evidence about whether drinking
milk can delay a stroke event or lower the hazard of dying from stroke.
Accelerated failure time models under Bayesian framework are convenient
tools that would help avoid worrying about the assumption of
proportional hazard normally required in a Cox proportional hazard model
and can directly show how faster/slower individuals in an exposure group
might have an event compared to others among different exposure groups
\citep{Wei1992, ibrahim2014b}.

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was
sponsored by the Ministry of Education, Sports, Science, and Technology
of Japan. Sampling methods and details about the JACC study have been
described extensively in the literature
\citep{Ohno2001, Tamakoshi2005, Tamakoshi2013}. Participants of the JACC
study completed self-administered questionnaires about their lifestyles,
food intake (food frequency questionnaire, FFQ), and medical histories
of cardiovascular disease or cancer. In the final follow-up of the JACC
study, data from a total of 110585 individuals (46395 men and 64190
women) were successfully retained for the current analysis. We further
excluded samples if they meet one of the following criteria: 1) with any
disease history of stroke, cancer, myocardial infarction, ischemic heart
disease, or other types heart disease (n = 6655, 2931 men and 3724
women); 2) did not answer the question regarding their milk consumption
in the baseline FFQ survey (n = 9545, 3593 men and 5952 women). Finally,
94385 (39386 men and 54999 women) are left in the database. The study
design and informed consent procedure were approved by the Ethics Review
Committee of Nagoya University School of Medicine.

@@

We calculated sex-specific means (standard deviation, sd) and proportion
of selected baseline characteristics according to the frequency of milk
intake. Age-adjusted stroke mortality rate were expressed as per 1000
person-year through the poisson regression model.

Full parametric proportional hazard models under Bayesian framework with
Weibull distribution were fitted using Just Another Gibbs Sampler (JAGS)
program \citep{Plummer2003} version 4.3.0 in R version 4.0.1
\citep{RCT2020}. JAGS program is similar to the OpenBUGS
\citep{Lunn2009} project that uses a Gibbs sampling engine for MCMC
simulation. In the current analysis, we specified non-informative prior
distributions for each of the parameters in our models
(\(\beta_n \sim N(0, 1000)\), and
\(\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)\)). The
Brooks-Gelman-Rubin diagnostic \citep{Brooks1998} was used to refine the
approximate point of convergence, the point when the ratio of the chains
is stable around 1 and the within and between chain variability start to
reach stability was visually checked. The auto-correlation tool further
identified if convergence has been achieved or if a high degree of
auto-correlation exists in the sample. Then, the number of iterations
discarded as `burn-in' was chosen. All models had a posterior sample
size of 100000 from four separated chains with a ``burn-in'' of 2500
iterations. Posterior means (sd) and 95\% Credible Intervals (CrI) of
the estimated hazard ratios (HRs) as well as acceleration factors (AFs)
were presented for each category of milk intake frequency taking the
``never'' category as the reference. Posterior probabilities that the
estimated hazard of dying from stroke for the milk intake for frequency
that higher or equal to ``1-2 times/month'' is smaller compared with
those who chose ``never'' to their milk intake frequency were calculated
as \(P(\text{HR} < 1)\).

@@

The total follow-up was 1555073 person-years (median = 19.3 years),
during which 2675 death from stroke was confirmed (1352 men and 1323
women). Among these stroke mortality, 952 were hemorrhagic stroke (432
men and 520 women), and 957 were cerebral infarction (520 men and 437
women). Age-adjusted stroke mortality rate for each category of milk
intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000
person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for
women.

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
chose ``never'' as their milk intake frequency at baseline, milk
drinkers were less likely to be a current smoker or a daily alcohol
consumer in both men and women. Furthermore, people consumed milk more
than 1-2 times/month were more likely to be a daily consumers of
vegetable, fruit as well as coffee, and more likely to join exercise
more than 1 hour/week among both sex.

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable-adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had slower speed and lower hazard of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
0.05; 95\% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95\% CrI: 0.85, 1.02)
compared with non-consumers. Chances that the posterior crude HRs were
estimated to be lower than 1 for those who had at least 1-2 times/month
was higher than 86.5\% in men and greater than 94.6\% in women. However,
lower hazard and delayed time-to-event was observed to remain after age
or multivariable adjustment only among daily male milk consumers.
Specifically, the mean (sd; 95\% CrI) of posterior
multivariable-adjusted AF and HR for daily male consumers of milk were
0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95\% CrI:
0.69, 0.93) with a probability of 99.0\% to be smaller than the null
value (=1). Daily female milk consumers had posterior AFs and HRs that
was distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88, 1.10) and
0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of chance
that their HRs could be smaller than 1.

@@

Some limitations here are worth mentioning. First, the milk intake
frequency as well as other lifestyle information was collected only once
at the baseline and was self-reported. Apparently habits in life are
possible to alter over the time and these would resulted in
misclassfication and residual confoudings. Second, despite reasonable
validity of FFQ in the JACC study cohort was assessed and confirmed,
measurement errors are inevitable. Therefore, we did not try to compute
the amount of consumption by multiplying an average volume per occasion
with the frequency of intake since the random error might be exaggerated
and the observed associations may have attenuated. Strengths of our
analyses included that we have transformed the research questions to
more transparent ones that is easier for interpretation. Direct
probabilities that daily milk intake is associated with lower hazard or
delayed stroke mortality event were provided here after thorough
computer simulation.

In conclusion, the JACC study database has provided evidence that
Japanese men who consumed milk daily had lower hazard of dying from
stroke especially cerebral infarction compared with their counterparts
who never consumed milk. Time before an event of stroke mortality
occurred were slowed down and delayed among men who drank milk
regularly.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{The authors declare no conflict of interest. The
founding sponsors had no role in the design of the study; in the
collection, analyses, or interpretation of data; in the writing of the
manuscript, an in the decision to publish the results.}

>>>>

Eastern Asian populations were reported to have higher burden from
either mortality or morbidity from stroke than populations in European
or American regions \citep{Kim2014}. Dairy food, especially milk has
been suggested to reduce stroke risk by nearly 7\% for each 200 g
increment of daily consumption \citep{DeGoede2016}. Although 2 daily
servings of milk or dairy products is recommended in Japan
\citep{Yoshiike2007}, the actual per capita intake (\(\approx\) 63
g/day) of these food groups is much lower and less frequent than that in
Western countries \citep{Saito2019}. Given that previous reports have
also indicated no significant
\citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
associations \citep{Larsson2009}, whether people with such a low level
intake of milk can still benefit against stroke would require
elucidation. A more intuitive interpretation would be available if we
were able to show the probabilities and how certain the existing data
can provide evidence about whether drinking milk can delay or lower the
hazard of dying from stroke. Accelerated failure time models under
Bayesian framework are convenient tools that would help avoid worrying
about the assumption of proportional hazard normally required in a Cox
proportional hazard model and can directly show how faster/slower
individuals in one exposure group might have an event compared to others
among different exposure groups \citep{Wei1992, ibrahim2014b}.

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was
sponsored by the Ministry of Education, Sports, Science, and Technology
of Japan. Sampling methods and details about the JACC study have been
described extensively in the literature
\citep{Ohno2001, Tamakoshi2005, Tamakoshi2013}. Participants of the JACC
study completed self-administered questionnaires about their lifestyles,
food intake (food frequency questionnaire, FFQ), and medical histories
of cardiovascular disease or cancer. In the final follow-up of the JACC
study, data from a total of 110585 individuals (46395 men and 64190
women) were successfully retained for the current analysis. We further
excluded samples if they meet one of the following criteria: 1) with any
disease history of stroke, cancer, myocardial infarction, ischemic heart
disease, or other types heart disease (n = 6655, 2931 men and 3724
women); 2) did not answer the question regarding their milk consumption
in the baseline FFQ survey (n = 9545, 3593 men and 5952 women). Finally,
94385 (39386 men and 54999 women) are left in the database. The study
design and informed consent procedure were approved by the Ethics Review
Committee of Hokkaido University School of Medicine.

@@

We calculated sex-specific means (standard deviation, sd) and proportion
of selected baseline characteristics according to the frequency of milk
intake. Age-adjusted stroke mortality rate were expressed as per 1000
person-year predicted through poisson regression models.

Full parametric proportional hazard models under Bayesian framework with
Weibull distribution were fitted using Just Another Gibbs Sampler (JAGS)
program \citep{Plummer2003} version 4.3.0 in R version 4.0.1
\citep{RCT2020}. JAGS program is similar to the OpenBUGS
\citep{Lunn2009} project that uses a Gibbs sampling engine for MCMC
simulation. In the current analysis, we specified non-informative prior
distributions for each of the parameters in our models
(\(\beta_n \sim N(0, 1000)\), and
\(\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)\)). The
Brooks-Gelman-Rubin diagnostic \citep{Brooks1998} was used to refine the
approximate point of convergence, the point when the ratio of the chains
is stable around 1 and the within and between chain variability start to
reach stability was visually checked. The auto-correlation tool further
identified if convergence has been achieved or if a high degree of
auto-correlation exists in the sample. Then, the number of iterations
discarded as `burn-in' was chosen. All models had a posterior sample
size of 100000 from four separated chains with a ``burn-in'' of 2500
iterations. Posterior means (sd) and 95\% Credible Intervals (CrI) of
the estimated hazard ratios (HRs) as well as acceleration factors (AFs)
were presented for each category of milk intake frequency taking the
``never'' category as the reference. Posterior probabilities that the
estimated hazard of dying from stroke for the milk intake for frequency
that higher or equal to ``1-2 times/month'' is smaller compared with
those who chose ``never'' to their milk intake frequency were calculated
as \(Pr(\text{HR} < 1)\).

@@

The total follow-up was 1555073 person-years (median = 19.3 years),
during which 2675 death from stroke was confirmed (1352 men and 1323
women). Among these stroke mortality, 952 were hemorrhagic stroke (432
men and 520 women), and 957 were cerebral infarction (520 men and 437
women). Age-adjusted stroke mortality rates for each category of milk
intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000
person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for
women.

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
chose ``never'' as their milk intake frequency at baseline, milk
drinkers were less likely to be a current smoker or a daily alcohol
consumer in both men and women. Furthermore, people consumed milk more
than 1-2 times/month were more likely to be a daily consumers of
vegetable, fruit as well as coffee, and more likely to join exercise
more than 1 hour/week among both sexes.

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable-adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had slower speed and lower hazard of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
0.05; 95\% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95\% CrI: 0.85, 1.02)
compared with non-consumers. Chances that the posterior crude HRs were
estimated to be lower than 1 for those who had at least 1-2 times/month
was higher than 86.5\% in men and greater than 94.6\% in women. However,
lower hazard and delayed time-to-event was observed to remain after age
or multivariable adjustment only among daily male milk consumers.
Specifically, the mean (sd; 95\% CrI) of posterior
multivariable-adjusted AF and HR for daily male consumers of milk were
0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95\% CrI:
0.69, 0.93) with a probability of 99.0\% to be smaller than the null
value (=1). Daily female milk consumers had posterior AFs and HRs that
were distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88, 1.10)
and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of
chance that their HRs could be smaller than 1.

@@

Some limitations here are worth mentioning. First, the milk intake
frequency as well as other lifestyle information was collected only once
at the baseline and was self-reported. Apparently life habits are
possible to alter over time and these would resulted in misclassfication
and residual confoundings. Second, despite reasonable validity of FFQ in
the JACC study cohort was assessed and confirmed, measurement errors are
inevitable. Therefore, we did not try to compute the amount of
consumption by multiplying an average volume per occasion with the
frequency of intake since the random error might be exaggerated and the
observed associations may have attenuated. Strengths of our analyses
included that we have transformed the research questions to more
transparent ones that is easier for interpretation. Direct probabilities
that daily milk intake is associated with lower hazard or delayed stroke
mortality event were provided here after thorough computer simulations.

In conclusion, the JACC study database has provided evidence that
Japanese men who consumed milk daily had lower hazard of dying from
stroke particularly cerebral infarction compared with their counterparts
who never consumed milk. Time before an event of stroke mortality
occurred were slowed down and delayed among men who drank milk
regularly.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{The authors declare no conflict of interest. The
funding sponsors had no role in the design of the study; in the
collection, analyses, or interpretation of data; in the writing of the
manuscript, an in the decision to publish the results.}
